Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-11 ch04-lrmhinf/ch04appendices.inc.tex
First corrections of Johan (CH04)

\section{\glsentrytext{AVIS} Measurement set-up}
\label{app:avis-setup}
The measurements of the \gls{AVIS} are carried out using a \Simulink model running at a sampling time of $\Ts = 1\unit{ms}$ as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis}.

@@

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption[\glsentrytext{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction.}
  \label{fig:avis:withAxes}
\end{figure}

>>>>

\section{\glsentrytext{AVIS} Measurement set-up}
\label{app:avis-setup}
The measurements of the \gls{AVIS} are carried out using a \Simulink model that configures the \gls{DAQ} card, implements a digital controller and provides some basic signal processing.
\Simulink executes the code, as shown in \figref{fig:avis:simulink:setup} and \figref{fig:avis:simulink:avis},  using a constant time step $\Ts = 1\unit{ms}$ on a real-time computer equipped with \code{xPC Target} (nowadays: \Simulink Real-Time).

@@

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption[\glsentrytext{AVIS} with coordinate frame, sensors and actuators.]{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors at each of the four corners. For each of the actuators and sensors, the color indicates the principal direction (x:red, y:green, z:blue).}
  \label{fig:avis:withAxes}
\end{figure}

### 2016-04-11 ch04-lrmhinf/lrmhinf.tex
TODO: colormatch avis photos
Shift hue in one of the AVIS pics
Externalize some frequency grids
 - also computed alpha, delta for example grid.
First corrections of Johan (CH04)

For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.

@@

Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation the \gls{LPM} \citep{Schoukens2009LPM} and \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.

@@

\section{Problem Formulation}
\label{sec:lrmhinf:Problem}
Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
The \Hinf{} norm of the error system $\Delta$ is
\begin{equation}
  \gamma 
     = 
       \infnorm{\Delta} 
    \isdef 
       \sup_{\omega} 
         \svdMax{\Delta(\omega)}
  \label{eq:lrmhinf:HinfNorm}
\end{equation}
for a stable system where $\svdMax{\placeholder}$ denotes the maximum singular value of $\placeholder$.
Note that for \gls{SISO} systems, $\svdMax{\Delta} = \abs{\Delta}$ and the definition above reduces to
\begin{equation}
  \gamma 
    = 
       \infnorm{\Delta} 
    \isdef 
         \sup_{\omega} 
         \abs{\Delta(\omega)}
  \text{ for \gls{SISO} systems}
  \text{.}
  \label{eq:lrmhinf:HinfNormSISO}
\end{equation}
In robust control design methodologies, such \Hinf{} norms often play an important purpose to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.

@@

To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
\begin{equation}
 \omega_{\star} 
     \isdef 
       \arg
         \sup_{\omega} 
           \svdMax{\Delta(\omega)}
  \text{.}
  \label{eq:lrmhinf:omega-star}
\end{equation}
However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid$.
As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
\begin{align}
  \gamma &\isdef 
    \sup_{\omega} 
      \svdMax{\Delta(\omega)}
         = \max 
             \Set{
                \max_{\omega \in \DFTGrid  } 
                  \svdMax{\Delta(\omega)}
                \;,\;
                \sup_{\omega \in \InterGrid} 
                  \svdMax{\Delta(\omega)}
                }
  \label{eq:lrmhinf:gamma-split-grid}\\
  \gammaAtGrid & \isdef 
    \max_{\omega \in \DFTGrid  } 
      \svdMax{\Delta(\omega)}
  \label{eq:lrmhinf:gamma:atGrid}\\
  \gammaIntergrid & \isdef 
    \sup_{\omega \in \InterGrid} 
      \svdMax{\Delta(\omega)}
   \label{eq:lrmhinf:gamma:interGrid}
\end{align}
where $\Omega \isdef \OpenInterval{0,\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
Direct inspection of the \gls{FRF} data only allows access to $\gammaAtGrid$.
Two cases can be distinguished:
\begin{enumerate}
  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
\end{enumerate}
The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
Its expected value over different realizations of the input signal $\expectedValue{\gammaAtGrid} \leq \gamma$ due to the limited frequency resolution.
Such an underestimate may lead to overly optimistic controller designs.

@@

\subsection{Set-up}
Consider an output-error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
For an infinitely long data record, this can be described in the time-domain as
\begin{equation}
  y_{\Delta}(n) 
    = 
      y_{\Delta0}(n)
      + v(n) 
    = 
      \Delta(q)u_{\Delta}(n) 
      + H(q)e(n)
  \label{eq:lrmhinf:sysDeltaInfData}
\end{equation}
where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
\begin{equation}
    y_{\Delta}(n) 
      = 
        \Delta(q)u(n) 
        + H(q)e(n) 
        + t_{\Delta}(n)
    \text{.}
    \label{eq:lrmhinf:sysDeltaFiniteData}
\end{equation}
By applying the \gls{DFT}
\begin{equation}
  X(k) 
       = 
         \frac{1}
              {\sqrt{N}} 
         \sum_{n=0}^{N-1} 
            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
         \quad   
         \forall k \in \mathbb{Z}
  \label{eq:lrmhinf:DFT}
\end{equation} 
to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
\begin{equation}
  Y_{\Delta}(k) 
                = 
                  \Delta(\omega_k) U_{\Delta}(k) 
                  + T_{\Delta}(\omega_k) 
                  + V(k) 
  \text{.}
  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
\end{equation}
The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.

@@

\subsection{The \glsentrydesc{LRM}}
\label{sec:lrmhinf:LRM}
The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:lrmhinf:sysDeltaFiniteDataFD} are smooth functions of the frequency.
As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
\begin{align}
  \Delta(\omega_{k+r})     
    &\approx 
        \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
      = 
        \frac{B_k(r)}{A_k(r)} 
      \isdef 
        \LocalModel{\Delta}_{k}(\omega_{k+r})
      \label{eq:lrmhinf:LRMTaylorSystem} \\
  T_{\Delta}(\omega_{k+r}) 
    &\approx 
        \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
      = 
        \frac{T_k'(r)}{A_k(r)} 
      \isdef 
        \LocalModel{T}_{k}(\omega_{k+r})
  \label{eq:lrmhinf:LRMTaylorTransient}
  \text{.}
\end{align}
Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \Set{-N_W,\ldots,+N_W}$ around each bin $k$.
This yields
\begin{equation}
  Y_{\Delta}(k+r) 
                 \approx
                    \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
                    + T_{\Delta}(\omega_{k+r}) 
    \quad
    \forall r \in \LocalWindow
    \text{.}
    \label{eq:lrmhinf:LocalWindowSpectra}
\end{equation}
By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
\begin{align}
  Y_{\Delta}(k+r) 
                  & \approx
                    \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
                    + \LocalModel{T}_k(\omega_{k+r}) 
                    & \forall r \in \LocalWindow \\
                  & = 
                    \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
                    + 
                    \frac{T'_k(r)}{A_k(r)} 
                    & \forall r \in \LocalWindow
    \text{.}
    \label{eq:lrmhinf:LocalWindowSpectraLRM}
\end{align}
To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
By doing so, the local linear-least-squares cost function
\begin{equation}
  \sum_{r=-N_W}^{N_W} 
  \left| 
    A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
  \right|^2
  \label{eq:lrmhinf:localCostLRM}
\end{equation}
 around each bin $k$ can be constructed.
We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.

@@

Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
In this chapter a Hann window and $N_S=1$ are used.
Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).

@@

\subsection{Study of the experiment length}
Frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.

We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $100$ samples to randomize the initial conditions.
To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.

@@

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption{Conceptual illustration of (active) vibration isolation set-ups. In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  % If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  % When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength\figurewidth{0.75\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
  \caption{\Glsentryfirst{AVIS}.}
  \label{fig:lrmhinf:avis}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.475\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}
  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}
  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
  The left photo shows one of the air mounts providing passive vibration isolation.
  The right photo shows two linear motors that play a role in the active vibration isolation.}
  \label{fig:lrmhinf:avis:details}
\end{figure}

@@

\section{Conclusions}
\label{sec:lrmhinf:conclusion}
A reliable \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.

>>>>

For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of a system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.

@@

Although important steps have been made in model-error-modeling, existing methods involve a trade-off between accuracy, measurement time, and user intervention.
The aim of this chapter is to develop a golden mean between traditional non-parametric techniques (third approach) and a full parametric model (second approach).
The proposed $\Hinf{}$ norm estimation procedure exploits recent developments in frequency domain estimation using the \gls{LPM} \citep{Schoukens2009LPM} and the \gls{LRM} \citep{McKelvey2012LRM} as introduced in \citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
Before, these \gls{LPM} and \gls{LRM} techniques have been used to enhance at-grid frequency response estimates.
Here, these methods are extended to provide both an at-grid and inter-grid evaluation of the maximum singular value near resonances, as is required for the $\Hinf{}$ norm and consequently the design of robust controllers.
The performance of these local parametric models in the context of robust control design is investigated, and bounds on the required measurement time to obtain a reliable estimate of the \Hinf{} norm are obtained.
% Preliminary results appear in~\citep{Geerardyn2014IFAC,Geerardyn2014ISMA}.
% This paper presents the full procedure, including more theoretical treatment of the $\Hinf{}$ norm estimation procedure, and a description of the required measurement time.

@@

\section{Problem Formulation}
\label{sec:lrmhinf:Problem}
Robust control based on \Hinf{} optimization requires a nominal parametric model $\estimated\Plant$ and a bound on the model error $\Delta$. 
After the model $\estimated\Plant$ is determined, either through first principles modeling or system identification, it remains to determine a bound on the model error $\Delta$.
The \Hinf{} norm of the error system $\Delta$ is
\begin{equation}
  \gamma 
     = 
       \infnorm{\Delta} 
    \isdef 
       \sup_{\omega} 
         \svdMax{\Delta(\omega)}
  \label{eq:lrmhinf:HinfNorm}
\end{equation}
for a stable system where $\svdMax{\placeholder}$ denotes the maximum singular value of $\placeholder$.
Note that for \gls{SISO} systems, $\svdMax{\Delta} = \abs{\Delta}$ and the definition above reduces to
\begin{equation}
  \gamma 
    = 
       \infnorm{\Delta} 
    \isdef 
         \sup_{\omega} 
         \abs{\Delta(\omega)}
  \text{ for \gls{SISO} systems}
  \text{.}
  \label{eq:lrmhinf:HinfNormSISO}
\end{equation}
In robust control design methodologies, such \Hinf{} norms often play an important role to specify the `size' of a model class for which the controller that is to be designed should meet certain requirements~\citep{Skogestad2005}.

@@

To estimate $\gamma$, only $\Delta(\omega_{\star})$ is of interest, where
\begin{equation}
 \omega_{\star} 
     \isdef 
       \arg
         \sup_{\omega} 
           \svdMax{\Delta(\omega)}
  \text{.}
  \label{eq:lrmhinf:omega-star}
\end{equation}
However, in a finite measurement time, non-parametric approaches only give access to a finite and discrete grid of frequencies $\omega_k \in \DFTGrid $, i.e. $\DFTGrid \isdef{\omega_1, \omega_2, \ldots, \omega_{N-1}}$.
As such, \eqref{eq:lrmhinf:HinfNorm} can be rewritten as
\begin{equation}
  \gamma \isdef 
    \sup_{\omega} 
      \svdMax{\Delta(\omega)}
         = \max 
             \Set{
                \max_{\omega \in \DFTGrid  } 
                  \svdMax{\Delta(\omega)}
                \;,\;
                \sup_{\omega \in \InterGrid} 
                  \svdMax{\Delta(\omega)}
                }
  \label{eq:lrmhinf:gamma-split-grid}
  \text{.}
\end{equation}
For convenience, we extract both contributions above as:
\begin{align}
  \gammaAtGrid & \isdef 
    \max_{\omega \in \DFTGrid  } 
      \svdMax{\Delta(\omega)}
  \label{eq:lrmhinf:gamma:atGrid}\\
  \gammaIntergrid & \isdef 
    \sup_{\omega \in \InterGrid} 
      \svdMax{\Delta(\omega)}
   \label{eq:lrmhinf:gamma:interGrid}
\end{align}
where $\Omega \isdef \OpenInterval{0,\frac{2\pi}{\Ts}}$ is the measured frequency range for a sampling time $\Ts$.
Direct inspection of the \gls{FRF} data only allows access to $\gammaAtGrid$.
Two cases can be distinguished:
\begin{enumerate}
  \item $\omega_{\star} \in \DFTGrid$ such that $\svdMax{\Delta(\omega_{\star})} = \gamma =\gamma_{\mathrm{FRF}}$ is observed directly on the discrete frequency grid,
  \item $\omega_{\star} \not\in \DFTGrid$, i.e. the extremal value $\svdMax{\Delta(\omega_{\star})}  = \gamma = \gammaIntergrid$ is determined by the inter-grid behavior.
\end{enumerate}
The use of $\gamma_{\mathrm{FRF}}$ is standard in \gls{FRF}-based approaches, e.g.~\citep{vandeWal2002}.
Its expected value over different realizations of the input signal $\expectedValue{\gammaAtGrid} \leq \gamma$ due to the limited frequency resolution.
Such an underestimate may lead to overly optimistic controller designs.

@@

\subsection{Set-up}
Consider an output error \gls{LTI} discrete-time \gls{SISO} system $\Delta(q)$ excited by an input signal $u_{\Delta}(n)$.
For an infinitely long data record, this can be described in the time-domain as
\begin{equation}
  y_{\Delta}(n) 
    = 
      y_{\Delta0}(n)
      + v(n) 
    = 
      \Delta(q)u_{\Delta}(n) 
      + H(q)e(n)
  \label{eq:lrmhinf:sysDeltaInfData}
\end{equation}
where $q^{-1}$ is the lag operator, $e(n)$ is white Gaussian noise with unity variance, and both $\Delta(q)$ and $H(q)$ are stable causal real-rational functions.
For a limited data record ($n \in \Set{0,\ldots,N-1}$), the transient contributions $t_{\Delta}(n)$ lead to:
\begin{equation}
    y_{\Delta}(n) 
      = 
        \Delta(q)u(n) 
        + H(q)e(n) 
        + t_{\Delta}(n)
    \text{.}
    \label{eq:lrmhinf:sysDeltaFiniteData}
\end{equation}
By applying the \gls{DFT}
\begin{equation}
  X(k) 
       = 
         \frac{1}
              {\sqrt{N}} 
         \sum_{n=0}^{N-1} 
            x(n) \exp \left( \frac{- j 2 \pi k n }{N} \right)
         \quad   
         \forall k \in \mathbb{Z}
  \label{eq:lrmhinf:DFT}
\end{equation} 
to both sides of~\eqref{eq:lrmhinf:sysDeltaFiniteData}, one obtains:
\begin{equation}
  Y_{\Delta}(k) 
                = 
                  \Delta(\omega_k) U_{\Delta}(k) 
                  + T_{\Delta}(\omega_k) 
                  + V(k) 
  \text{.}
  \label{eq:lrmhinf:sysDeltaFiniteDataFD}
\end{equation}
The $T_{\Delta}$ contribution models the difference between the begin and end conditions of the filters $\Delta$ and $H$ in the measurement~\citep{Pintelon1997ARB}.
The index $k$ corresponds to the $k^{\text{th}}$ frequency bin with frequency $\omega_{k} = 2\pi k / (N \Ts)$ such that the frequency grid $\DFTGrid \isdef \Set{\left.\omega_k \right| k = 1,\ldots,N-1}$.

@@

\subsection{The \glsentrydesc{LRM}}
\label{sec:lrmhinf:LRM}
\TODO{remove whole LRM section in favor for \chapref{sec:nonparametric}}
The local models $\LocalModel{\Delta}_k$ are estimated using the \gls{LRM}~\citep{McKelvey2012LRM}.
The \gls{LRM} exploits the fact that the transfer function $\Delta(\omega)$ and the leakage term $T_{\Delta}(\omega)$  in \eqref{eq:lrmhinf:sysDeltaFiniteDataFD} are smooth functions of the frequency.
As such, $\Delta$ and $T_{\Delta}$ are approximated locally by rational functions around each bin $k$:
\begin{align}
  \Delta(\omega_{k+r})     
    &\approx 
        \frac{\sum_{i=0}^{N_{B}} b_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}} 
      = 
        \frac{B_k(r)}{A_k(r)} 
      \isdef 
        \LocalModel{\Delta}_{k}(\omega_{k+r})
      \label{eq:lrmhinf:LRMTaylorSystem} \\
  T_{\Delta}(\omega_{k+r}) 
    &\approx 
        \frac{\sum_{i=0}^{N_{T}} t_{i}(k) r^{i}}{1 + \sum_{i=1}^{N_{A}} a_{i}(k) r^{i}}  
      = 
        \frac{T_k'(r)}{A_k(r)} 
      \isdef 
        \LocalModel{T}_{k}(\omega_{k+r})
  \label{eq:lrmhinf:LRMTaylorTransient}
  \text{.}
\end{align}
Its local parameters $a_{i}(k)$, $b_{i}(k)$ and $t_{i}(k)$ are estimated by considering~\eqref{eq:lrmhinf:sysDeltaFiniteDataFD} in the local window $\LocalWindow = \Set{-N_W,\ldots,+N_W}$ around each bin $k$.
This yields
\begin{equation}
  Y_{\Delta}(k+r) 
                 \approx
                    \Delta(\omega_{k+r}) U_{\Delta}(k+r) 
                    + T_{\Delta}(\omega_{k+r}) 
    \quad
    \forall r \in \LocalWindow
    \text{.}
    \label{eq:lrmhinf:LocalWindowSpectra}
\end{equation}
By substituting the local models $\LocalModel{\Delta}_k$ and $\LocalModel{T}_k$, one obtains
\begin{align}
  Y_{\Delta}(k+r) 
                  & \approx
                    \LocalModel{\Delta}_k(\omega_{k+r}) U_{\Delta}(k+r) 
                    + \LocalModel{T}_k(\omega_{k+r}) 
                    & \forall r \in \LocalWindow \\
                  & = 
                    \frac{B_k(r)}{A_k(r)} U_{\Delta}(k+r) 
                    + 
                    \frac{T'_k(r)}{A_k(r)} 
                    & \forall r \in \LocalWindow
    \text{.}
    \label{eq:lrmhinf:LocalWindowSpectraLRM}
\end{align}
To make this expression linear in the parameters $a_i(k)$, both sides are multiplied by $A_k(r)$ as in~\citep{Levy1959}.
By doing so, the local linear-least-squares cost function
\begin{equation}
  \sum_{r=-N_W}^{N_W} 
  \left| 
    A_k(r) Y_{\Delta}(k+r) - B_k(r) U_{\Delta}(k+r) - T'_{k}(r)
  \right|^2
  \label{eq:lrmhinf:localCostLRM}
\end{equation}
 around each bin $k$ can be constructed.
We denote $\lrm{N_W,N_B,N_A,N_T}$ to be the \gls{LRM} with the orders $N_B$, $N_A$, $N_T$ and bandwidth $N_W$ defined above.
For $N_A=0$ the \gls{LRM} simplifies to the \gls{LPM} which we shall denote as $\lpm{N_W,N_B,N_T}$.

@@

Classical \gls{SA} techniques~\citep{Bendat1993} can estimate the \gls{FRF} of $\Delta$.
This is done by first splitting the input/output signals into $N_S$ segments of ${N}/{N_S}$ samples, windowing the segments to reduce leakage and applying the \gls{DFT}.
By dividing the resulting output/input spectra, the \gls{FRF} is obtained.
\TODO{formules}
In this chapter a Hann window and $N_S=1$ are used.
Note that $N_S>1$  increases the measurement time by a factor $N_S$ to attain the same frequency resolution (but would improve  transient and noise rejection).

@@

\subsection{Study of the experiment length}
The frequency resolution, and hence the experiment length, is key to obtain a reliable \Hinf{} norm estimate.
In this section, we determine the minimal experiment length needed for the proposed approach by means of simulations.

We simulate the system \eqref{eq:lrmhinf:O2sysDT} for $16\,100$ samples and discard the first $2\tau=100$ samples to randomize the initial conditions.
To mimic the effect of progressively measuring longer data records, the first remaining $N$ samples are used to estimate $\infnorm{\Delta}$ as in \secref{sec:lrmhinf:LPMHinf}.
The values of $N \in \ClosedInterval{35,16\,000}$ are chosen such that $\expectedValue{\gamma_{\mathrm{FRF}}(N)}$ is a non-decreasing function of $N$.
This ensures that grid misalignment between the actual resonance frequency and the observed frequency grid is accounted for such that the worst-case estimate of the resonance is obtained.
These simulations are then repeated in a Monte Carlo simulation of $n_{\mathrm{MC}}=200$ runs where each run has a different realization of  $u_{\Delta}(n)$ and $v(n)$.
The resulting sample average and standard deviation $\sigma$ are shown in \figref{fig:lrmhinf:MC-run-length}.

@@

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Traditional set-up.}  
    \label{fig:lrmhinf:vibration-isolation:traditional}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Principle of sky-hook damping.}  
    \label{fig:lrmhinf:vibration-isolation:skyhook}
  \end{subfigure}
  \disclaimer{Figure based on \citep[Fig. 3 and 4]{Voorhoeve2015SYSID} and \citep[Fig. 3 and 6]{Karnopp1995}.}
  \caption[Vibration isolation set-ups (traditional, sky-hook dampinng)]{Conceptual illustration of (active) vibration isolation set-ups. In addition to the passive isolation (spring and damper), the active controller $C$ provides additional isolation using the measurement of the payload velocity ($y=v_z$).
  % If the velocity relative to ground is measured (a), the controller design involves trading-off which disturbance should be suppressed better.
  % When the absolute velocity the payload is measured (b), the controller can suppress both disturbances as it acts as a damper between a virtual fixed point (``sky'') and the payload.
  }
  \label{fig:lrmhinf:vibration-isolation}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength\figurewidth{0.75\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/avis.jpg}
  \caption{\Glsentryfirst{AVIS}.}
  \label{fig:lrmhinf:avis}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.475\columnwidth}
  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-airmount-cropped.jpg}
  \includegraphics[width=\figurewidth]{\thisDir/figs/avis-motors-cropped.jpg}
  \caption[\glsentrytext{AVIS} isolation module.]{Isolation module of the \glsentrytext{AVIS}. 
  The left photo shows one of the air mounts providing passive vibration isolation.
  The right photo shows two linear motors that play a role in the active vibration isolation.}
  \label{fig:lrmhinf:avis:details}
\end{figure}

@@

\section{Conclusions}
\label{sec:lrmhinf:conclusion}
A reliable local parametric \Hinf{} norm estimation technique for high performance, non-conservative robust control design is investigated.
In this paper, a new approach is presented that employs so-called local parametric \gls{LRM} models that lead to an enhanced estimate of $\infnorm{\Delta}$ of a \gls{SISO} error system by interpolating between neighboring local models.
It is also shown that the \gls{LPM} is not a worthwhile alternative to the \gls{LRM} to estimate $\infnorm{\Delta}$.
